Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-15 paper/sec-analysis.tex

In this section we describe our analysis strategy.
%
First of all, we discuss the settings
for jet clustering  and the strategy for $b$-tagging.
%
Then we discuss the categorisation of events in different
topologies and how to prioritise among them.
%
We motivate our choice of analysis cuts by comparing signal and background
for representative kinematical distributions.
%
Finally, we describe the simulation of PU and validate
the PU subtraction strategy that we adopt.

@@

After the  parton shower, final state particles
are clustered using the
jet reconstruction algorithms
obtained from
{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
{\tt v3.1.0}.
%
We use different types of jet definitions:
\begin{itemize}
\item {\it Small-$R$ jets}.

  These are jets  reconstructed with the
  anti-$k_T$ clustering algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
  %
  These small-$R$ jets are required
  to have transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$, within the central 
  acceptance of ATLAS and CMS, the region
  where $b$-tagging is possible.

@@

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
  conditions.
  %
  We use the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
  %
  Before applying the MDT, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen (C/A)
  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
  with $R=1.2$.

@@

  These subjets are constructed by reclustering the constituents
  of a large-$R$ jet, again with the
  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter, namely
  $R=0.3$~\cite{Aad:2015uka}.
 %
  These small-$R$ subjets will be the main input for
  $b$-tagging in the boosted category.
  %
  They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
  %
\end{itemize}

In addition, we have
also explored the possible improvements
in the analysis from the use
of variable-$R$ jets~\cite{Krohn:2009zg}, finding
a similar performance as in the case of fixed-$R$ jets.
%
This is explained by the fact that
variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can
differ substantially~\cite{Cacciari:2008gd},
such as in heavy resonance
searches~\cite{Aad:2015fna},
where the degree of boost of the final state
is {\it a priori} unknown.

@@

  This variable is defined by reclustering the constituents of a jet with the
  $k_t$ algorithm~\cite{Ellis:1993tq},
  which usually clusters last the harder constituents, and then
  taking the $k_t$ distance measure between the two subjets at the final stage of the recombination
  procedure,
  \be
  \label{eq:ktsplitting}
\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, .
\ee
with $p_{T,1}$ and $p_{T,2}$ the transverse momenta of the two subjets merged
in the final step of the clustering, and $\Delta R_{12}$ the corresponding
angular separation.

@@

  The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
  of a jet with the exclusive $k_t$ algorithm~\cite{Catani:1993hr}
  and requiring that $N$ subjets are found,
  \be
  \tau_N \equiv \frac{1}{d_0} \sum_k p_{T,k}\cdot {\rm min}\lp \delta R_{1k}, \ldots,
  \delta R_{Nk}\rp \, , \qquad d_0\equiv \sum_k p_{T,k}\cdot R \, ,
  \ee
  with $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
  subjet $i$ to constituent $k$.
  %
  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
  \be
  \label{eq:tau21}
\tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
  \ee
  which provides good discrimination 
  between QCD jets and jets arising from the decay of
  a heavy resonance.

@@

In this analysis we adopt
a $b$-tagging strategy along the lines
of current ATLAS performance~\cite{Aad:2013gja,Aad:2015ydr},
though differences with respect to
the corresponding CMS
settings~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
do not modify qualitatively our results.
%
For each type of jet definition used, a different
$b$-tagging strategy is adopted:

@@

  We attempt to $b$-tag only the four (two) hardest small-$R$ jets
  in the resolved (intermediate) category.
  %
  Trying to $b$-tag all the
  small-$R$ jets that satisfy the acceptance cuts worsens the
  overall performance
  due to combinatorics.

@@

    As in the case
    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
    else one finds a degradation of the
    signal significance due to combinatorics.
    %
    The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.

@@

Concerning the values of the $b$-tag probability, $f_b$, and
the $b$-mistag probability of light and charm jets, $f_l$ and  $f_c$
respectively,
we used the values $f_b=0.8$, $f_l=0.01$
and  $f_c=0.1$.

@@

The present analysis follows a strategy similar to the
scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we aim to consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
This approach is robust
under variations of
the underlying production model of Higgs pairs is modified,
for instance in the case of
BSM dynamics, which can substantially increase
the degree of boost of the final state.

@@

  An event which
  contains at least two large-$R$ jets, with the two leading jets
 being $b$-tagged.
 %
 Each of these two large-$R$, $b$-tagged, jets are 
 thus candidates
 to contain the decay products of a Higgs boson.

@@

  An event with exactly one large-$R$, $b$-tagged, jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two small-$R$, $b$-tagged, jets,
  which must be separated with respect to the large-$R$ jet
  by an angular distance of $\Delta R\ge 1.2$.
  %

@@

 An event with at least
  four $b$-tagged small-$R$ jets.
  %
  The two Higgs candidates are reconstructed out of the
  leading four small-$R$ jets in the event
  by considering all possibilities of forming two pairs of jets
  and then choosing the configuration that minimizes the relative difference of
  dijet masses.
  %

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
around the nominal Higgs boson mass of $m_h= 125$
GeV.
%
In particular we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser than the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}.
%
The motivation
for this choice 
is that further improvements of the
signal significance will be obtained using an MVA.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

These three categories are not exclusive:
a given event can be assigned to more than one category, for
example, satisfying the requirements of both the intermediate
and resolved
categories at the same time.
%
The exception is the boosted and intermediate categories, which have
orthogonal jet selection requirements.
%
The optimization of the analysis
of the three categories is performed inclusively, and
then events are exclusively assigned to specific category
starting with the one with the highest signal significance.

The separate optimisation of the three categories needs to be performed in
a inclusive analysis, and then we introduce a
 priorisation starting with the category of highest signal significance.

 This has been achieved as follows.
 %
First of all we perform an inclusive analysis, and optimise the
signal significance
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that the category with higher significance is
the boosted one,
followed by the intermediate and the resolved ones, the latter two
with similar significance.
%
Therefore, for the final analysis, we turn to an exclusive approach:
if an event satisfies the boosted requirements, it is assigned to
this category, else we check if it suits the intermediate
requirements.
%
It the event also fails the intermediate category
requirements, we
then check if it pass the resolved selection criteria.
%
The resulting exclusive event samples are then separately processed
through the MVA, allowing a consistent combination
of the significance of the three event categories.

@@

We now motivate the values of
kinematic cuts applied to the different categories, 
comparing representative kinematic distributions between
signal and background events.
%
We first present results without PU, and then
discuss
the impact of PU
on the description of the various kinematic
distributions.
%
In the following, all
distributions will be normalized to their total integral.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
 \includegraphics[width=0.48\textwidth]{plots/pt_H0_bst_C1d_noPU.pdf}
 \includegraphics[width=0.48\textwidth]{plots/pt_H1_bst_C1d_noPU.pdf}
\caption{\small  Comparison of the $p_T$ distributions of the
  leading (left) and
  subleading (right) large-$R$ jets in the boosted category,
  in signal and background events.
  %
  Distributions have been normalized to unity.
  %
  The total background is the sum of all components
  listed in Table~\ref{tab:samples}.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Turning to the resolved category, an important aspect to account
in the corresponding selection
cuts is the fact that the $p_T$ distribution
of the four leading small-$R$ jets of the event can be relatively soft,
specially for the subleading jets.
%
As noted in~\cite{deLima:2014dta}, this is a consequence of the fact
that in general the boost from the Higgs decays is moderate.
%
These considerations lead to the requirement that the $p_T$
selection
for the small-$R$ jets cannot be too large.
%
In Fig.~\ref{fig:cutplots23}
we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events: we observe that both
distributions are peaked at $p_T \le 50$ GeV, with the signal distribution
eventually becoming dominant at large $p_T$.
%
The feasibility to being able to trigger on four small-$R$ jets with a relatively
soft $p_T$ distribution is one of the experimental challenges for
exploiting the resolved category in this final state,
and hence the requirement that $p_T \ge 40$ GeV for
the small-$R$ jets.
%
In  Fig.~\ref{fig:cutplots23} we also show the
rapidity distribution of the the small-$R$
jets in the resolved category.
%
As expected, the production
is mostly central, more in the case
of signal events, since backgrounds are dominated by
QCD $t$-channel exchange, and thus the
selection criteria on the jet rapidity  are highly efficient.

@@

One of the selection cuts with highest discrimination power is the requirement
that the invariant mass of the Higgs candidate (di)jets must lie within a window
around the nominal Higgs value, Eq.~(\ref{higgsmasswindow}).
%
In Fig.~\ref{fig:mHHinv} we show the invariant mass
of the leading reconstructed Higgs candidates, before the Higgs mass window
selection
  is applied, for the resolved and boosted categories.
%
While the signal distribution is of course peaked at the
nominal Higgs mass, the background distributions
show no particular
structure.
%
The
width of the Higgs mass peak is driven both from QCD effects,
such as initial-state radiation (ISR)
and out-of-cone radiation, as well
as from the four-momenta smearing applied to final state particles.
%

@@

Another important kinematic distribution for
this process is the invariant mass
of the di-Higgs system.
%
This is a direct measure of the boost of the system,
which in  BSM scenarios can be substantially
enhanced, for instance due to
specific $d=6$ EFT operators~\cite{Azatov:2015oxa}.
%
One important advantage of the $b\bar{b}b\bar{b}$ final state for
di-Higgs production is that it significantly increases the reach
in $m_{hh}$ as compared to other channels with smaller branching
ratios,
such as $2b2\gamma$ or $2b2\tau$.
%
In Fig.~\ref{fig:mhh} we show the invariant mass distribution of the
reconstructed Higgs pairs,
comparing the resolved and the boosted categories.

@@

In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as compared
to the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this using the MVA.
%
For the boosted category the overall trend of the $m_{hh}$ distribution
is different because of the jet selection criteria, and the
distribution now peaks at higher values of the invariant mass.
%
In this case, signal and background distributions
look similar.
%
Note that at parton-level the $m_{hh}$ distribution
for signal events has a kinematic
cut-off at $m_{hh}^{\rm min}=250$ GeV, which is smeared due
to 
the parton shower and to detector resolution effects.
%

In Fig.~\ref{fig:pthh} we show the transverse momentum of
the di-Higgs system, $p_T^{hh}$,
for the resolved and boosted categories.
%
Again we see that the background has a steeper $p_T^{hh}$ distribution
that the signal, in both categories, thus this variable
should provide additional discrimination power, and therefore
this distribution is one of the inputs for the MVA.
%
In our LO simulation the $p_T^{hh}$ distribution is generated
by the parton shower, and improved theoretical
description would require
either the matching with higher-multiplicity
matrix elements~\cite{Maierhofer:2013sha} or
the full NLO calculation~\cite{Frederix:2014hta},
%
Nevertheless, as we will show,
the MVA shows only limited sensitivity to this variable, so its
modelling is not crucial in this specific application.

@@

We now study the discrimination power to separate signal
and background events contained in
jet substructure
variables.
%
In Fig.~\ref{fig:mva_substructure_1}
we show the distributions of representative
 substructure variables for the boosted category: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), 
the ECF ratio $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), and
the 2--to--1 subjettiness ratio $\tau_{12}$, Eq.~(\ref{eq:tau21}),
all for the leading
Higgs candidates, and also $\tau_{12}$ for the subleading
Higgs candidates.

@@

From Fig.~\ref{fig:mva_substructure_1}
we can observe how for these substructure variables the shapes of the signal
and background distributions reflect
the inherent differences in the internal structure of jets
between QCD jets and jets originated from the Higgs decays.
%
Signal and background distributions peak
in rather
different regions: for example, the $k_t$ splitting scale $\sqrt{d_{12}}$
peaks around 80 GeV (40 GeV) for signal (background) events, while
the distribution of the
ECF ratio $C_2^{(\beta)}$ is concentrated at small values
for signal but is much broader for background events.
%
From Fig.~\ref{fig:mva_substructure_1} we also see
the distributions of the subjettiness ratio $\tau_{12}$ are
reasonably similar
for both the leading and the subleading jets.
%
Therefore, while we do not explicitly have cuts in the substructure
variables, their discrimination power between signal and
background events is the motivation to include them
as input to the MVA, as discussed in Sect.~\ref{sec:mva}.

@@

Here we turn to discuss how the description of kinematic
distributions for $hh\to 4b$ signal
and background processes are
modified in a high pile-up (PU) environment.
%
To study the impact of PU,
Minimum Bias (MB) events,
including Multiple Parton Interactions (MPI), have been generated
with {\tt Pythia8}, and then
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios,
one with a mean number of
PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
with $\la n_{\rm PU}\ra=150$.
%
While the latter is closer to the HL-LHC forecasts,
we adopt $\la n_{\rm PU}\ra=80$ as our baseline,
given that it
is beyond the scope of this paper to fully optimize
the PU subtraction.

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} is based on eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.
%
From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
We apply {\tt SoftKiller}
to particles at the end of the parton shower, before
jet clustering.

>>>>

In this section we describe our analysis strategy.
%
First of all we discuss the settings
for jet clustering and the strategy for jet $b$-tagging.
%
Following this we discuss the categorisation of events into different
topologies, and how the different topologies may be prioritised.
%
We motivate our choice of analysis cuts by comparing signal and background
distributions for representative kinematic variables.
%
Finally, we describe the simulation of PU and validate
the PU subtraction strategy that we adopt.

@@

After the parton shower, final state particles
are clustered using the
jet reconstruction algorithms
of
{\tt FastJet}~\cite{Cacciari:2011ma,Cacciari:2005hq},
{\tt v3.1.0}.
%
Here we use the following jet definitions:
\begin{itemize}
\item {\it Small-$R$ jets}.

  These are jets  reconstructed with the
  anti-$k_T$ clustering algorithm~\cite{Cacciari:2008gp} with $R=0.4$ radius.
  %
  These small-$R$ jets are required
  to have transverse momentum $p_T \ge 40$~GeV
  and pseudo-rapidity $|\eta|<2.5$, within the central 
  acceptance of ATLAS and CMS, and therefore within the region
  where $b$-tagging is possible.

@@

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
  conditions, where the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$ are used.
  %
  Before applying the BDRS tagger, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen (C/A)
  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
  with $R=1.2$.

@@

  These subjets are constructed by reclustering the constituents
  of a large-$R$ jet, again with the
  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter, namely
  $R=0.3$~\cite{Aad:2015uka}. They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
 %
  These small-$R$ subjets will be the main input for
  $b$-tagging in the boosted category.
  %
\end{itemize}

We have
also explored the possible improvements
in the analysis from the use
of variable-$R$ jets~\cite{Krohn:2009zg}, finding
a similar performance as in the case of fixed-$R$ jets.
%
This is explained by the fact that
variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can
differ substantially~\cite{Cacciari:2008gd},
such as in heavy resonance
searches~\cite{Aad:2015fna},
where the degree of boost of the final state
is {\it a priori} unknown.

@@

  This variable is obtained by reclustering the constituents of a jet with the
  $k_t$ algorithm~\cite{Ellis:1993tq},
  which usually clusters last the harder constituents, and then
  taking the $k_t$ distance measure between the two subjets at the final stage of the recombination
  procedure,
  \be
  \label{eq:ktsplitting}
\sqrt{d_{12}} \equiv {\rm min}\lp p_{T,1},p_{T,2}\rp \cdot \Delta R_{12} \, .
\ee
with $p_{T,1}$ and $p_{T,2}$ the transverse momenta of the two subjets merged
in the final step of the clustering, and $\Delta R_{12}$ the corresponding
angular separation.

@@

  The $N$-subjettiness variables $\tau_N$ are defined by clustering the constituents
  of a jet with the exclusive $k_t$ algorithm~\cite{Catani:1993hr}
  and requiring that $N$ subjets are found,
  \be
  \tau_N \equiv \frac{1}{d_0} \sum_k p_{T,k}\cdot {\rm min}\lp \delta R_{1k}, \ldots,
  \delta R_{Nk}\rp \, , \qquad d_0\equiv \sum_k p_{T,k}\cdot R \, ,
  \ee
  where $p_{T,k}$ is the $p_T$ of the constituent particle $k$ and $\delta R_{ik}$ the distance from
  subjet $i$ to constituent $k$.
  %
  In this work we use as input to the MVA the ratio of 2-subjettiness to 1-subjettiness
  \be
  \label{eq:tau21}
\tau_{21} \equiv \frac{\tau_2}{\tau_1} \, ,
  \ee
  which provides good discrimination 
  between QCD jets and jets arising from the decay of
  a heavy resonance.

@@

In this analysis we adopt
a $b$-tagging strategy along the lines
of current ATLAS performance~\cite{Aad:2013gja,Aad:2015ydr},
though differences with respect to
the corresponding CMS
settings~\cite{Khachatryan:2011wq,Chatrchyan:2012jua}
do not modify qualitatively our results.
%
For each jet definition described above, a different
$b$-tagging strategy is adopted:

@@

  We attempt to $b$-tag only the four (two) hardest small-$R$ jets
  in the resolved (intermediate) category.
  %
  Attempting to $b$-tag all of the
  small-$R$ jets that satisfy the acceptance cuts worsens the
  overall performance as the probability of fake $b$-tags increases
  substantially.

@@

    As in the case
    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
    else one finds a degradation of the
    signal significance.
    %
    The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.

@@

For the $b$-tagging probability $f_b$, along with
the $b$-mistag probability of light ($f_l$) and charm ($f_c$) jets,
we used the values $f_b=0.8$, $f_l=0.01$
and  $f_c=0.1$.

@@

The present analysis follows a strategy similar to the
scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we aim to consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
This approach is robust
under variations of
the underlying production model of Higgs pairs,
for instance in the case of
BSM dynamics, which can substantially increase
the degree of boost in the final state.

@@

  An event which
  contains at least two large-$R$ jets, with the two leading jets
 being $b$-tagged.
 %
 Each of these two large-$R$, $b$-tagged, jets are 
 therefore candidates
 to contain the decay products of a Higgs boson.

@@

  An event with exactly one large-$R$, $b$-tagged jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two small-$R$, $b$-tagged, jets,
  which must be separated with respect to the large-$R$ jet
  by an angular distance of $\Delta R\ge 1.2$.
  %

@@

 An event with at least
  four $b$-tagged small-$R$ jets.
  %
  The two Higgs candidates are reconstructed out of the
  leading four small-$R$ jets in the event
  by considering all possible combinations of forming two pairs of jets
  and then choosing the configuration that minimizes the relative difference of
  dijet masses.
  %

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
GeV.
%
Specifically we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser than the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}.
%
The motivation
for such a loose cut 
is that further improvements of the
signal significance will be obtained using an MVA.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

These three categories are not exclusive:
a given event can be assigned to more than one category, for
example, satisfying the requirements of both the intermediate
and resolved
categories at the same time.
%
The exception is the boosted and intermediate categories, which have
conflicting jet selection requirements.
%

The separate optimisation of the three categories needs to be performed in
a inclusive analysis, following which we introduce a
 prioritisation whereby events are assigned an exclusive category starting 
 with the category of highest signal significance.

 This has been achieved as follows.
 %
First of all we perform an inclusive analysis, and optimise the
signal significance
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that the category with highest significance is
the boosted one,
followed by the intermediate and the resolved topologies, the latter two
with similar significance.
%
Therefore, when ascertaining which category an event is to be exclusively placed:
if the event satisfies the boosted requirements, it is assigned to
this category, else we check if it suits the intermediate
requirements.
%
It the event also fails the intermediate category
requirements, we
then check if it pass the resolved selection criteria.
%
The resulting exclusive event samples are then separately processed
through the MVA, allowing a consistent combination
of the significance of the three event categories.

@@

We now motivate the
kinematic cuts applied to the different categories, 
comparing representative kinematic distributions between
signal and background events.
%
Firstly we present results without PU, and then
discuss
the impact of PU
on the description of the various kinematic
distributions.
%
In the following, all
distributions will be normalized to their total integral.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
 \includegraphics[width=0.48\textwidth]{plots/pt_H0_bst_C1d_noPU.pdf}
 \includegraphics[width=0.48\textwidth]{plots/pt_H1_bst_C1d_noPU.pdf}
\caption{\small  Comparison of the $p_T$ distributions of the
  leading (left) and
  subleading (right) large-$R$ jets in the boosted category,
  for signal and background events.
  %
  Distributions have been normalized to unity.
  %
  The total background is the sum of all components
  listed in Table~\ref{tab:samples}.
}
\label{fig:cutplots1}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Turning to the resolved category, an important aspect to account for
in the corresponding selection
cuts is the fact that the $p_T$ distribution
of the four leading small-$R$ jets of the event can be relatively soft,
specially for the subleading jets.
%
As noted in~\cite{deLima:2014dta}, this is a consequence of the fact
that in general the boost from the Higgs decays is moderate.
Therefore the $p_T$ selection cuts for the small-$R$ jets cannot be too large.
%
In Fig.~\ref{fig:cutplots23}
we show the distribution in $p_T$ of the four leading
small-$R$ jets in signal and background events: we observe that both
distributions peak at $p_T \le 50$ GeV, with the signal distribution
eventually becoming dominant at large $p_T$.
%
The feasibility of triggering on four small-$R$ jets with a relatively
soft $p_T$ distribution is one of the experimental challenges for
exploiting the resolved category in this final state,
and hence the requirement that $p_T \ge 40$ GeV for
the small-$R$ jets.
%
In  Fig.~\ref{fig:cutplots23} we also show the
rapidity distribution of the the small-$R$
jets in the resolved category.
%
As expected, the production
is mostly central, more so in the case
of signal events, since backgrounds are dominated by
QCD $t$-channel exchange, therefore the
selection criteria on the jet rapidity are very efficient.

@@

One of the most discriminating selection cuts is the requirement
that the invariant mass of the Higgs candidate (di)jets must lie within a window
around the nominal Higgs value, Eq.~(\ref{higgsmasswindow}).
%
In Fig.~\ref{fig:mHHinv} we show the invariant mass
of the leading reconstructed Higgs candidates, before the Higgs mass window
selection
  is applied, for the resolved and boosted categories.
%
While the signal distribution naturally peaks at the
nominal Higgs mass, the background distributions
show no particular
structure.
%
The
width of the Higgs mass peak is driven both from QCD effects,
such as initial-state radiation (ISR)
and out-of-cone radiation, as well
as from the four-momentum smearing applied to final state particles
as part of our minimal detector simulation.
%

@@

The invariant mass of the di-Higgs system is another important
kinematic distribution for this process.
%
Thie di-Higgs invariant mass is a direct measure of the boost of the system,
which in  BSM scenarios can be substantially
enhanced, for instance due to
specific $d=6$ EFT operators~\cite{Azatov:2015oxa}.
%
One important advantage of the $b\bar{b}b\bar{b}$ final state for
di-Higgs production is that it significantly increases the reach
in $m_{hh}$ as compared to other channels with smaller branching
ratios,
such as $2b2\gamma$ or $2b2\tau$.
%
In Fig.~\ref{fig:mhh} we show the invariant mass distribution of the
reconstructed Higgs pairs,
comparing the resolved and the boosted categories.

@@

In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as compared
to the background,
and therefore one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this using the MVA.
%
For the boosted category the overall trend of the $m_{hh}$ distribution
is different because of the jet selection criteria, and the
distribution now peaks at higher values of the invariant mass.
%
In this case, signal and background distributions are not significantly
differentiated.
%
Note that at parton-level the $m_{hh}$ distribution
for signal events has a kinematic
cut-off at $m_{hh}^{\rm min}=250$ GeV, which is smeared due
to 
the parton shower and to detector resolution effects.
%

In Fig.~\ref{fig:pthh} we show the transverse momentum of
the di-Higgs system, $p_T^{hh}$,
for the resolved and boosted categories.
%
Once more we see that the background has a steeper fall-off in $p_T^{hh}$
than the signal, in both categories, therefore this variable
should provide additional discrimination power, motivating it's inclusion
as one of the inputs for the MVA.
%
In our LO simulation the $p_T^{hh}$ distribution is generated
by the parton shower, and improved theoretical
description would require
either the matching with higher-multiplicity
matrix elements~\cite{Maierhofer:2013sha} or
the full NLO calculation~\cite{Frederix:2014hta},
%
Nevertheless, as we will show,
the MVA shows only limited sensitivity to this variable, so its
modelling is not crucial in this specific application.

@@

We shall now investigate the discrimination power provided by jet substructure
quantities.
%
In Fig.~\ref{fig:mva_substructure_1}
we show the distributions of representative
 substructure variables for the boosted category: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), 
the ECF ratio $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), and
the 2--to--1 subjettiness ratio $\tau_{12}$, Eq.~(\ref{eq:tau21}),
all for the leading
Higgs candidates, and also $\tau_{12}$ for the subleading
Higgs candidates.

@@

From Fig.~\ref{fig:mva_substructure_1}
we can observe how for these substructure variables the shapes of the signal
and background distributions reflect
the inherent differences in the internal structure of jets
between QCD jets and jets originating from the Higgs decays.
%
Signal and background distributions peak
in rather
different regions. For example, the $k_t$ splitting scale $\sqrt{d_{12}}$
peaks around 80 GeV (40 GeV) for signal (background) events, while
the distribution of the
ECF ratio $C_2^{(\beta)}$ is concentrated at small values
for signal but is much broader for background events.
%
From Fig.~\ref{fig:mva_substructure_1} we also see
the distributions of the subjettiness ratio $\tau_{12}$ are
reasonably similar
for both the leading and the subleading jets.
%
Therefore, while we do not explicitly have cuts in the substructure
variables, their discrimination power between signal and
background events is the motivation to include them
as input to the MVA, as discussed in Sect.~\ref{sec:mva}.

@@

Now we turn to discuss how the description of kinematic
distributions for $hh\to 4b$ signal
and background processes are
modified in the presence of pile-up (PU).
%
To study the impact of PU,
Minimum Bias (MB) events,
including Multiple Parton Interactions (MPI), have been generated
with {\tt Pythia8}, and then
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios,
one with a mean number of
PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$, and another
with $\la n_{\rm PU}\ra=150$.
%
While the latter is closer to the HL-LHC forecasts,
we adopt $\la n_{\rm PU}\ra=80$ as our baseline,
given that it
is beyond the scope of this paper to fully optimize
the PU subtraction.

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} consists of eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.
%
From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
jet clustering.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.63\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
events in the resolved category, comparing the results without PU,
with PU $\la n_{\rm PU}\ra=80$. The distribution is then compared with and without SK subtraction.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%
